### 2019-12-17 report/05-stability.Rmd
Minor modification to the SEM

- Main results:
  - Richness destabilizes communities 
  - Turnover destabilizes communities, latter increased by enrichment
  - Trophic level decreased CV but increase species synchrony!:
  - Connectance!

@@

```{r}
lav_data %>%
  ggplot(aes(x = log_rich, y = MDS1)) +
  geom_point() +
  labs(x = "Log of species richness", y = "Axis of composition")

@@

```{r, fig.cap = "Biomass"}
prod_sem <- psem(
  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data),
  lme(MDS2 ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width, random = ~ 1 | basin, data = lav_data)
)
sumup_prod <- summary(prod_sem, .progressBar = F)
sumup_prod$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

@@

```{r colin_prod}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + MDS2, random = ~ 1 | basin, data = lav_data))
```

>>>>

- Main results:
  - Richness destabilizes communities 
  - Turnover destabilizes communities, latter increased by enrichment
  - Trophic level decreased CV but increase species synchrony!
  - Connectance!

@@

@@

```{r, fig.cap = "Biomass"}
prod_sem <- psem(
  lme(temperature_med ~ alt, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + DBO_med + temperature_med, random = ~ 1 | basin, data = lav_data)
)
sumup_prod <- summary(prod_sem, .progressBar = F)
sumup_prod$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

@@

```{r colin_prod}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data))
```
